---
title: "Covid-19 Growth Rates"
author: "Albin Abraham"
date: "5/3/2020"
output: html_document
---

##Introduction


Claim : If a county has a higher density, then it would have a higher number of positive tests per population. 

Converse : If a county has a higher density, then it would have a lower number of positive tests per population. 

Other Claims : 
Temperature affects infection rates.
  - need more data to make conclusions.

Possible Applications of this data?
  - predict the way certain restrictive policies are implemented in the future
    - more dense areas would have more restrictions. 


##Methodology:

What was our reasoning behind our study/actions?
Why these counties?
How did we collect our data?
What did we analize and why?
Why choose 28 days/ points for our data?
Difficulty of extending the days? 
Why not use Anova? probably use a similar response to Peter Dracopoulos.
Talk of our Labeling system if needed.
How we organized them
Why we organized them into BigTen Data frame.  


##Issues with data during analysis
Need more counties to normalize data and make a better conclusion
wait to run study so that we would have more days
Day 0? should it be moved to another location?
We wanted to look at humidity and it was not possible to obtain a proper data frame for temperature. 
  - obstacles with aquiring data.
  
Testing issues and possible errs for data
  - delays in testing 
  - data points are missrepresented 
  - hospitals reporting false deaths for incentives.

Data could be biased cause if communtiy is closed for longer, hospitals would have less tests.



```{r setup, include=FALSE}
# set up of each data frame (counties)
knitr::opts_chunk$set(echo = TRUE)
######################################################################################################
################################################# SETUP ##############################################
######################################################################################################
setwd("/Users/a2/Downloads/College/Stats/382") #Step 1
zdata <-read.csv("Covid_Cases.csv") 

######################################################################################################
####################################### COUNTY DATA FRAME SETUP ######################################
######################################################################################################

#1# Jefferson County starts on March 25th & ends on April 21st ####################################################################

JFD <- subset(zdata, zdata$State == "AL" & zdata$County.Name == "Jefferson County")
JFD <- JFD[5:length(JFD)]
JFD <- t(JFD)
colnames(JFD) <- "Cases"
JFD <- as.data.frame(JFD)
JFD <- subset(JFD, JFD$Cases > 100 & JFD$Cases <= 700)

#2# Contra Costa County starts on March 25th & ends on April 21st #################################################################

CCD <- subset(zdata, zdata$State == "CA" & zdata$County.Name == "Contra Costa County")
CCD <- CCD[5:length(CCD)]
CCD <- t(CCD)
colnames(CCD) <- "Cases"
CCD <- as.data.frame(CCD)
CCD <- subset(CCD, CCD$Cases > 100 & CCD$Cases < 750)
length(CCD$Cases)
#3# LA County starts on March 17th & ends on April 13th ###########################################################################

LAD <- subset(zdata, zdata$State == "CA" & zdata$County.Name == "Los Angeles County")
LAD <- LAD[5:length(LAD)]
LAD <- t(LAD)
colnames(LAD) <- "Cases"
LAD <- as.data.frame(LAD)
LAD <- subset(LAD, LAD$Cases > 100 & LAD$Cases < 10000)

#4# Philadelphia County starts on March 23rd & ends on April 19th #################################################################

PHD <- subset(zdata, zdata$State == "PA" & zdata$County.Name == "Philadelphia County")
PHD <- PHD[5:length(PHD)]
PHD <- t(PHD)
colnames(PHD) <- "Cases"
PHD <- as.data.frame(PHD)
PHD <- subset(PHD, PHD$Cases > 100 & PHD$Cases < 9000)

#5# Queens County starts on March 16th & ends on April 12th #######################################################################

QND <- subset(zdata, zdata$State == "NY" & zdata$County.Name == "Queens County")
QND <- QND[5:length(QND)]
QND <- t(QND)
colnames(QND) <- "Cases"
QND <- as.data.frame(QND)
QND <- subset(QND, QND$Cases > 100 & QND$Cases < 33000)

#6# Cook County starts on March 17th & ends on April 13th #########################################################################

CKD <- subset(zdata, zdata$State == "IL" & zdata$County.Name == "Cook County")
CKD <- CKD[5:length(CKD)]
CKD <- t(CKD)
colnames(CKD) <- "Cases"
CKD <- as.data.frame(CKD)
CKD <- subset(CKD, CKD$Cases > 100 & CKD$Cases < 16000)

#7# Miami County starts on March 19th & ends on April 15th ########################################################################

MDD <- subset(zdata, zdata$State == "FL" & zdata$County.Name == "Miami-Dade County")
MDD <- MDD[5:length(MDD)]
MDD <- t(MDD)
colnames(MDD) <- "Cases"
MDD <- as.data.frame(MDD)
MDD <- subset(MDD, MDD$Cases > 100 & MDD$Cases < 8300)

#8# King County starts on March 9th & ends on April 5th ###########################################################################

KGD <- subset(zdata, zdata$State == "WA" & zdata$County.Name == "King County")
KGD <- KGD[5:length(KGD)]
KGD <- t(KGD)
colnames(KGD) <- "Cases"
KGD <- as.data.frame(KGD)
KGD <- subset(KGD, KGD$Cases > 100 & KGD$Cases < 3200)

#9# Harris County starts on March 25th & ends on April 21st #######################################################################

HAD <- subset(zdata, zdata$State == "TX" & zdata$County.Name == "Harris County")
HAD <- HAD[5:length(HAD)]
HAD <- t(HAD)
colnames(HAD) <- "Cases"
HAD <- as.data.frame(HAD)
HAD <- subset(HAD, HAD$Cases > 100 & HAD$Cases < 5000)

#10# Wayne County starts on March 19th & ends on April 15th #######################################################################

WAD <- subset(zdata, zdata$State == "MI" & zdata$County.Name == "Wayne County")
WAD <- WAD[5:length(WAD)]
WAD <- t(WAD)
colnames(WAD) <- "Cases"
WAD <- as.data.frame(WAD)
WAD <- subset(WAD, WAD$Cases > 100 & WAD$Cases < 13000)
WAD
length(WAD$Cases)


JFD$Day <- 0:27
CCD$Day <- 0:27
LAD$Day <- 0:27
PHD$Day <- 0:27
QND$Day <- 0:27
CKD$Day <- 0:27
MDD$Day <- 0:27
KGD$Day <- 0:27
HAD$Day <- 0:27
WAD$Day <- 0:27

JFD[,c("Day","Cases")] -> JFD
CCD[,c("Day","Cases")] -> CCD
LAD[,c("Day","Cases")] -> LAD
PHD[,c("Day","Cases")] -> PHD
QND[,c("Day","Cases")] -> QND
CKD[,c("Day","Cases")] -> CKD
MDD[,c("Day","Cases")] -> MDD
KGD[,c("Day","Cases")] -> KGD
HAD[,c("Day","Cases")] -> HAD
WAD[,c("Day","Cases")] -> WAD



######################################################################################################
###################################### TOTAL # INFECTION DAY 27 ######################################
######################################################################################################

rep(JFD[28,2],28)->JFD$Day27Infections
rep(CCD[28,2],28)->CCD$Day27Infections
rep(LAD[28,2],28)->LAD$Day27Infections
rep(PHD[28,2],28)->PHD$Day27Infections
rep(QND[28,2],28)->QND$Day27Infections
rep(CKD[28,2],28)->CKD$Day27Infections
rep(MDD[28,2],28)->MDD$Day27Infections
rep(KGD[28,2],28)->KGD$Day27Infections
rep(HAD[28,2],28)->HAD$Day27Infections
rep(WAD[28,2],28)->WAD$Day27Infections

######################################################################################################
########################################## TEMPERATURE DATA ##########################################
######################################################################################################

JFD$TEMP <- c(75,83,84,85,76,74,60,67,72,78,80,82,84,73,80,77,62,73,73,67,63,62,70,77,67,59,73,77)
CCD$TEMP <- c(58,59,60,58,59,66,69,65,67,67,59,53,53,65,67,63,68,62,71,75,80,83,71,63,66,68,64,72)
LAD$TEMP <- c(62,65,64,66,68,71,67,66,65,62,66,68,68,76,77,74,69,70,70,64,63,65,63,56,65,72,62,66)
PHD$TEMP <- c(45,59,47,60,69,57,53,55,48,56,58,57,56,70,58,58,74,66,49,57,59,71,60,54,51,53,49,62)
QND$TEMP <- c(46,53,53,51,70,64,46,41,52,46,57,66,51,49,53,47,55,59,51,61,63,66,66,63,56,49,56,60)
CKD$TEMP <- c(48,45,64,63,32,35,45,45,59,52,48,63,64,48,41,49,56,64,56,47,62,80,66,48,50,62,66,56)
MDD$TEMP <- c(80,80,80,80,80,80,83,82,82,79,82,82,87,85,77,79,80,81,81,82,85,91,92,81,83,84,85,86)
KGD$TEMP <- c(51,53,51,50,40,45,47,57,56,57,62,63,57,61,49,48,50,49,49,55,55,51,50,49,48,49,55,56)
HAD$TEMP <- c(88,86,87,80,81,83,75,74,75,79,70,73,76,86,89,92,74,76,90,71,69,69,74,81,74,82,83,85)
WAD$TEMP <- c(49,63,37,39,41,43,56,57,47,50,63,48,44,49,61,62,59,56,58,69,70,50,44,57,61,54,41,37)

######################################################################################################
###################################### AVERAGE TEMPERATURE DATA ######################################
######################################################################################################

rep(mean(JFD$TEMP),28) -> JFD$AveTemp
rep(mean(CCD$TEMP),28) -> CCD$AveTemp
rep(mean(LAD$TEMP),28) -> LAD$AveTemp
rep(mean(PHD$TEMP),28) -> PHD$AveTemp
rep(mean(QND$TEMP),28) -> QND$AveTemp
rep(mean(CKD$TEMP),28) -> CKD$AveTemp
rep(mean(MDD$TEMP),28) -> MDD$AveTemp
rep(mean(KGD$TEMP),28) -> KGD$AveTemp
rep(mean(HAD$TEMP),28) -> HAD$AveTemp
rep(mean(WAD$TEMP),28) -> WAD$AveTemp

######################################################################################################
############################################### E-score ##############################################
######################################################################################################

JFD$Escore <- rep(1.30,28)
JFD$Escore <- rep(1.30,28)
CCD$Escore <- rep(25.0,28)
LAD$Escore <- rep(39.6,28)
PHD$Escore <- rep(15.0,28)
QND$Escore <- rep(29.5,28)
CKD$Escore <- rep(76.8,28)
MDD$Escore <- rep(20.8,28)
KGD$Escore <- rep(21.9,28)
HAD$Escore <- rep(20.0,28)
WAD$Escore <- rep(16.8,28)


######################################################################################################
##################################### Mean Distance From an Airport ##################################
######################################################################################################

JFD$MeanDistance<-rep(28.76,28)
CCD$MeanDistance<-rep(12.77,28)
LAD$MeanDistance<-rep(12.77,28)
PHD$MeanDistance<-rep(20.44,28)
QND$MeanDistance<-rep(16.30,28)
CKD$MeanDistance<-rep(15.87,28)
MDD$MeanDistance<-rep(12.16,28)
KGD$MeanDistance<-rep(18.85,28)
HAD$MeanDistance<-rep(16.15,28)
WAD$MeanDistance<-rep(21.35,28)


######################################################################################################
################################################### Area #############################################
######################################################################################################


JFD$Area<-rep(1124,28)
CCD$Area<-rep(716,28)
LAD$Area<-rep(4058,28)
PHD$Area<-rep(134,28)
QND$Area<-rep(109,28)
CKD$Area<-rep(945,28)
MDD$Area<-rep(1899,28)
KGD$Area<-rep(2116,28)
HAD$Area<-rep(1703,28)
WAD$Area<-rep(612,28)


######################################################################################################
################################################ Population ##########################################
######################################################################################################


JFD$Population <- rep(0.659,28)
CCD$Population <- rep(1.154,28)
LAD$Population <- rep(10.04,28)
PHD$Population <- rep(1.584,28)
QND$Population <- rep(2.273,28)
CKD$Population <- rep(5.15,28)
MDD$Population <- rep(2.717,28)
KGD$Population <- rep(2.253,28)
HAD$Population <- rep(4.713,28)
WAD$Population <- rep(1.749,28)

######################################################################################################
################################################# Density ############################################
######################################################################################################

JFD$Population/JFD$Area -> JFD$Density
CCD$Population/CCD$Area -> CCD$Density
LAD$Population/LAD$Area -> LAD$Density
PHD$Population/PHD$Area -> PHD$Density
QND$Population/QND$Area -> QND$Density
CKD$Population/CKD$Area -> CKD$Density
MDD$Population/MDD$Area -> MDD$Density
KGD$Population/KGD$Area -> KGD$Density
HAD$Population/HAD$Area -> HAD$Density
WAD$Population/WAD$Area -> WAD$Density

######################################################################################################
############################################### Closed Days ##########################################
######################################################################################################

JFD$DaysClosed <- rep(24,28)
CCD$DaysClosed <- rep(28,28)
LAD$DaysClosed <- rep(27,28)
PHD$DaysClosed <- rep(28,28)
QND$DaysClosed <- rep(22,28)
CKD$DaysClosed <- rep(24,28)
MDD$DaysClosed <- rep(14,28)
KGD$DaysClosed <- rep(21,28)
HAD$DaysClosed <- rep(20,28)
WAD$DaysClosed <- rep(23,28)


```

###Focus in on new york and Chicago

Data :

  Tasks : 
    Make box plot of infection rates
    Make box plot of total number of infetions
    Make box plot of infections per density
    
    Make histograms for individual county cases
    

``` {r data analysis}
######################################################################################################
#################################### Daily Infection / Population ####################################
######################################################################################################

x <- sequence(28)

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (JFD$`Cases`[i+1] - JFD$`Cases`[i])}
JFD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (CCD$`Cases`[i+1] - CCD$`Cases`[i])}
CCD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (LAD$`Cases`[i+1] - LAD$`Cases`[i])}
LAD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (PHD$`Cases`[i+1] - PHD$`Cases`[i])}
PHD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (QND$`Cases`[i+1] - QND$`Cases`[i])}
QND$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (CKD$`Cases`[i+1] - CKD$`Cases`[i])}
CKD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (MDD$`Cases`[i+1] - MDD$`Cases`[i])}
MDD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (KGD$`Cases`[i+1] - KGD$`Cases`[i])}
KGD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (HAD$`Cases`[i+1] - HAD$`Cases`[i])}
HAD$InfectionsByDay <- tempv

tempv <- sequence(28)
for(i in x){
  tempv[i] <- (WAD$`Cases`[i+1] - WAD$`Cases`[i])}
WAD$InfectionsByDay <- tempv

####################################################################################################
################################ Average Infections Per Day Per Pop ################################
####################################################################################################

JFD$InfectionsByDay / JFD$Population -> JFD$PositiveTestPerPop
CCD$InfectionsByDay / CCD$Population -> CCD$PositiveTestPerPop
LAD$InfectionsByDay / LAD$Population -> LAD$PositiveTestPerPop
PHD$InfectionsByDay / PHD$Population -> PHD$PositiveTestPerPop
QND$InfectionsByDay / QND$Population -> QND$PositiveTestPerPop
CKD$InfectionsByDay / CKD$Population -> CKD$PositiveTestPerPop
MDD$InfectionsByDay / MDD$Population -> MDD$PositiveTestPerPop
KGD$InfectionsByDay / KGD$Population -> KGD$PositiveTestPerPop
HAD$InfectionsByDay / HAD$Population -> HAD$PositiveTestPerPop
WAD$InfectionsByDay / WAD$Population -> WAD$PositiveTestPerPop


rep(mean(JFD$PositiveTestPerPop[1:27]),28) -> JFD$AverageInfPerDay
rep(mean(CCD$PositiveTestPerPop[1:27]),28) -> CCD$AverageInfPerDay
rep(mean(LAD$PositiveTestPerPop[1:27]),28) -> LAD$AverageInfPerDay
rep(mean(PHD$PositiveTestPerPop[1:27]),28) -> PHD$AverageInfPerDay
rep(mean(QND$PositiveTestPerPop[1:27]),28) -> QND$AverageInfPerDay
rep(mean(CKD$PositiveTestPerPop[1:27]),28) -> CKD$AverageInfPerDay
rep(mean(MDD$PositiveTestPerPop[1:27]),28) -> MDD$AverageInfPerDay
rep(mean(KGD$PositiveTestPerPop[1:27]),28) -> KGD$AverageInfPerDay
rep(mean(HAD$PositiveTestPerPop[1:27]),28) -> HAD$AverageInfPerDay
rep(mean(WAD$PositiveTestPerPop[1:27]),28) -> WAD$AverageInfPerDay


JFD$AverageInfPerDay/JFD$Population -> JFD$AvInfPerPop
CCD$AverageInfPerDay/CCD$Population -> CCD$AvInfPerPop
LAD$AverageInfPerDay/LAD$Population -> LAD$AvInfPerPop
PHD$AverageInfPerDay/PHD$Population -> PHD$AvInfPerPop
QND$AverageInfPerDay/QND$Population -> QND$AvInfPerPop
CKD$AverageInfPerDay/CKD$Population -> CKD$AvInfPerPop
MDD$AverageInfPerDay/MDD$Population -> MDD$AvInfPerPop
KGD$AverageInfPerDay/KGD$Population -> KGD$AvInfPerPop
HAD$AverageInfPerDay/HAD$Population -> HAD$AvInfPerPop
WAD$AverageInfPerDay/WAD$Population -> WAD$AvInfPerPop

####################################################################################################
############################### Average Infections Per Day Per Area ################################
####################################################################################################
JFD$Cases / JFD$Area -> JFD$CasesPerArea
CCD$Cases / CCD$Area -> CCD$CasesPerArea
LAD$Cases / LAD$Area -> LAD$CasesPerArea
PHD$Cases / PHD$Area -> PHD$CasesPerArea
QND$Cases / QND$Area -> QND$CasesPerArea
CKD$Cases / CKD$Area -> CKD$CasesPerArea
MDD$Cases / MDD$Area -> MDD$CasesPerArea
KGD$Cases / KGD$Area -> KGD$CasesPerArea
HAD$Cases / HAD$Area -> HAD$CasesPerArea
WAD$Cases / WAD$Area -> WAD$CasesPerArea

JFD$Cases / (JFD$Density*1000000) -> JFD$CasesPerDensity
CCD$Cases / (CCD$Density*1000000) -> CCD$CasesPerDensity
LAD$Cases / (LAD$Density*1000000) -> LAD$CasesPerDensity
PHD$Cases / (PHD$Density*1000000) -> PHD$CasesPerDensity
QND$Cases / (QND$Density*1000000) -> QND$CasesPerDensity
CKD$Cases / (CKD$Density*1000000) -> CKD$CasesPerDensity
MDD$Cases / (MDD$Density*1000000) -> MDD$CasesPerDensity
KGD$Cases / (KGD$Density*1000000) -> KGD$CasesPerDensity
HAD$Cases / (HAD$Density*1000000) -> HAD$CasesPerDensity
WAD$Cases / (WAD$Density*1000000) -> WAD$CasesPerDensity

JFD$InfectionsByDay / JFD$Area -> JFD$PositiveTestPerArea
CCD$InfectionsByDay / CCD$Area -> CCD$PositiveTestPerArea
LAD$InfectionsByDay / LAD$Area -> LAD$PositiveTestPerArea
PHD$InfectionsByDay / PHD$Area -> PHD$PositiveTestPerArea
QND$InfectionsByDay / QND$Area -> QND$PositiveTestPerArea
CKD$InfectionsByDay / CKD$Area -> CKD$PositiveTestPerArea
MDD$InfectionsByDay / MDD$Area -> MDD$PositiveTestPerArea
KGD$InfectionsByDay / KGD$Area -> KGD$PositiveTestPerArea
HAD$InfectionsByDay / HAD$Area -> HAD$PositiveTestPerArea
WAD$InfectionsByDay / WAD$Area -> WAD$PositiveTestPerArea

JFD$InfectionsByDay / (JFD$Density*1000000) -> JFD$PositiveTestPerDensity
CCD$InfectionsByDay / (CCD$Density*1000000) -> CCD$PositiveTestPerDensity
LAD$InfectionsByDay / (LAD$Density*1000000) -> LAD$PositiveTestPerDensity
PHD$InfectionsByDay / (PHD$Density*1000000) -> PHD$PositiveTestPerDensity
QND$InfectionsByDay / (QND$Density*1000000) -> QND$PositiveTestPerDensity
CKD$InfectionsByDay / (CKD$Density*1000000) -> CKD$PositiveTestPerDensity
MDD$InfectionsByDay / (MDD$Density*1000000) -> MDD$PositiveTestPerDensity
KGD$InfectionsByDay / (KGD$Density*1000000) -> KGD$PositiveTestPerDensity
HAD$InfectionsByDay / (HAD$Density*1000000) -> HAD$PositiveTestPerDensity
WAD$InfectionsByDay / (WAD$Density*1000000) -> WAD$PositiveTestPerDensity

######################################################################################################
#################################### Day 27 Infections Per Population ################################
######################################################################################################

100*JFD$Day27Infections/(JFD$Population*10000000) -> JFD$Day27PercentPositives
100*CCD$Day27Infections/(CCD$Population*10000000) -> CCD$Day27PercentPositives
100*LAD$Day27Infections/(LAD$Population*10000000) -> LAD$Day27PercentPositives
100*PHD$Day27Infections/(PHD$Population*10000000) -> PHD$Day27PercentPositives
100*QND$Day27Infections/(QND$Population*10000000) -> QND$Day27PercentPositives
100*CKD$Day27Infections/(CKD$Population*10000000) -> CKD$Day27PercentPositives
100*MDD$Day27Infections/(MDD$Population*10000000) -> MDD$Day27PercentPositives
100*KGD$Day27Infections/(KGD$Population*10000000) -> KGD$Day27PercentPositives
100*HAD$Day27Infections/(HAD$Population*10000000) -> HAD$Day27PercentPositives
100*WAD$Day27Infections/(WAD$Population*10000000) -> WAD$Day27PercentPositives

######################################################################################################
######################################## 10 County Data Frames #######################################
######################################################################################################

as.data.frame(matrix(nrow=10,ncol=10,0)) -> BigTen
rownames(BigTen)<-c("Jefferson", "Contra Costa", "Los Angeles","Philadelphia","Queens","Cook","Miami-Dade","King","Harris","Wayne")
colnames(BigTen)<-c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")
BigTen[1,]<-JFD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[2,]<-CCD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[3,]<-LAD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[4,]<-PHD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[5,]<-QND[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[6,]<-CKD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[7,]<-MDD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[8,]<-KGD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[9,]<-HAD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen[10,]<-WAD[1,c("Day27PercentPositives","AvInfPerPop", "AveTemp","Escore","MeanDistance","Area","Population","Density", "DaysClosed","Day27Infections")]
BigTen

BigTenAnalysis <- BigTen[,c("Day27PercentPositives","AvInfPerPop","AveTemp","Escore","MeanDistance","Density","DaysClosed")]

BigTenAnalysis

summary(lm(formula = BigTen$Day27Infections~BigTen$AveTemp+BigTen$Escore + BigTen$MeanDistance + BigTen$Density + BigTen$DaysClosed-1))

```

``` {r Graphs}
##########################################################################################
######################################### Graphs #########################################
##########################################################################################

#Boxplots for all cases in all ten counties 
#  - explain that it looks the way it does due to a lack of data sets(counties)
#  - if we use more samples then there would be a more normalized distribution
#    - if this is done effectively, then perhaps a better conclusion could have been drawn.

#Boxplots for Average number of infections per Density for all counties
#  - explain why this does not account for all possible variables related to this study
#  - explain how/why density would make up for the errs in this graph
#  - accounting for density accounts for regions that are in need of intervention

#Boxplot for Average number of infection rates for all counties
#  - The boxplot helps identify outliers for Average number of infection rates 
#  - An analysis of the individual counties would help us distinguish the impact of different variables. 
#  - Example :
#     - We would want to check outlier communities with low average infection rates to see if a specific variable was causing/correlated to this decrease(outlier)
#     - if enough outliers were to be analyzed and support a particular claim/policy then that data would suggest that it is an effective policy

# Calculate Average number of cases per county and store that as one vector
AverageCases <- sequence(10)
AverageCases[1] <- JFD$Day27Infections[1]
AverageCases[2] <- HAD$Day27Infections[1]
AverageCases[3] <- KGD$Day27Infections[1]
AverageCases[4] <- LAD$Day27Infections[1]
AverageCases[5] <- CKD$Day27Infections[1]
AverageCases[6] <- QND$Day27Infections[1]
AverageCases[7] <- MDD$Day27Infections[1]
AverageCases[8] <- WAD$Day27Infections[1]
AverageCases[9] <- CCD$Day27Infections[1]
AverageCases[10] <- PHD$Day27Infections[1]
boxplot(AverageCases, col = "purple", main = "Average Number of Cases Per County", ylab = "Cases")

AvCasesPerDensity <- c(1:10)
AvCasesPerDensity[1] <- AverageCases[1]/(JFD$Density[1] * 1000000)
AvCasesPerDensity[2] <- AverageCases[2]/(HAD$Density[1] * 1000000)
AvCasesPerDensity[3] <- AverageCases[3]/(KGD$Density[1] * 1000000)
AvCasesPerDensity[4] <- AverageCases[4]/(LAD$Density[1] * 1000000)
AvCasesPerDensity[5] <- AverageCases[5]/(CKD$Density[1] * 1000000)
AvCasesPerDensity[6] <- AverageCases[6]/(QND$Density[1] * 1000000)
AvCasesPerDensity[7] <- AverageCases[7]/(MDD$Density[1] * 1000000)
AvCasesPerDensity[8] <- AverageCases[8]/(WAD$Density[1] * 1000000)
AvCasesPerDensity[9] <- AverageCases[9]/(CCD$Density[1] * 1000000)
AvCasesPerDensity[10] <- AverageCases[10]/(PHD$Density[1] * 1000000)
boxplot(AvCasesPerDensity, col = "blue", main = "Average Number of Cases Per Density", ylab = "Cases/Density")

AverageInfectionRates <- c(1:10)
JFD$AverageInfPerDay[1] -> AverageInfectionRates[1]
CCD$AverageInfPerDay[1] -> AverageInfectionRates[2]
LAD$AverageInfPerDay[1] -> AverageInfectionRates[3]
PHD$AverageInfPerDay[1] -> AverageInfectionRates[4]
QND$AverageInfPerDay[1] -> AverageInfectionRates[5]
CKD$AverageInfPerDay[1] -> AverageInfectionRates[6]
MDD$AverageInfPerDay[1] -> AverageInfectionRates[7]
KGD$AverageInfPerDay[1] -> AverageInfectionRates[8]
HAD$AverageInfPerDay[1] -> AverageInfectionRates[9]
WAD$AverageInfPerDay[1] -> AverageInfectionRates[10]
boxplot(AvCasesPerDensity, col = "red", main = "Average Rate of Infection per County", ylab = "Infection Rates")

# T tests

#t.test(BigTen$AvInfPerPop)      # Average infection Rates / population size for each respective county
#t.test(AverageCases)            # Average number of cases per county
#t.test(AverageInfectionRates)   # Average Infection Rates per county of the 28 day timespan
#t.test(AvCasesPerDensity)       # Average Cases per density of each respective county

#Graph Order 

# Analysis of Results
#1.) Pairs analysis 
#    - show possible correlations and state why density is used to adjust graphs
#    - why are we using density accounted measurement to rank(compare) variables. 

# Linear Regression

#2.) Graph of Cases Per Day
#  - explain reasoning why New York is on top and suggest comparing variables while accounting for density will draw more accurate conclusions.
#    - based on pairs analysis

#3.) Graph of Cases per Density # Miami will be on top
#  - Present Density graph and explain reasoning

# use these variables to show a corelation to exposer
#4.) Graph of Cases per Density with Temperature Ranking
#  - Since Data set is small there may not be a valid conclusion to be drawn from this case

#5.) Graph of Cases per Density with Escore
#  - Since Data set is small there may not be a valid conclusion to be drawn from this case

#6.) Graph of Cases per Density with mean Distance
#  - Since Data set is small there may not be a valid conclusion to be drawn from this case

#7.) Graph of Cases per Density with days closed
#  - Since Data set is small there may not be a valid conclusion to be drawn from this case

#8.) Graph of Individual Counties and explain why chicago and New York need further analysis.

#9.) Graph of Counties Positive tests per Density overlapped
#   - propose new study/ another way to ana


pairs(BigTenAnalysis)
######################################################################################################
################################## Linear Regression & Analysis ######################################
######################################################################################################
# Linear regression on Increase of cases/population size per day.
summary(lm(formula = BigTen$Day27Infections~BigTen$AveTemp+BigTen$Escore + BigTen$MeanDistance + BigTen$Density + BigTen$DaysClosed))

# helps show correlation with density
# other variables aren't as conclusive since our data does not have enough data entries.

par(mfrow = c(1,1))
par(mar = c(5,5,2,2)) # alters the margins and prevent possible margin errors.


scatter.smooth(HAD$Day,HAD$Cases, type="o", col="white",ylim = c(0,35000),xlab = "Day", ylab = "Confirmed Cases", main = "Covid-19 Cases", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$Cases~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$Cases~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$Cases~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$Cases~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$Cases~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$Cases~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$Cases~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$Cases~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$Cases~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)

legend(1, 35000, legend=c("Contra Costa County", "LA County", "Philadelphia County", "Queen's County", "Cook County", "Miami-Dade County", "King County", "Harris County", "Wayne County", "Jefferson County"), col=c("red", "green","orange", "yellow", "purple", "dark green", "brown", "black", "dark red", "blue"), lty=1, cex=0.9)


#********* use this (the graph below) to rank all of the ranking variables
# explain how we processed this variable. 
# explain all of the factors related to each county

# MDD had highest point

scatter.smooth(HAD$Day,HAD$CasesPerDensity, type="o", col="white",ylim = c(0,6),xlab = "Day", ylab = "Positive Test/Density", main = "Number of Cases/Density", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$CasesPerDensity~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$CasesPerDensity~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$CasesPerDensity~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$CasesPerDensity~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$CasesPerDensity~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$CasesPerDensity~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$CasesPerDensity~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$CasesPerDensity~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$CasesPerDensity~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)
legend(1, 6, legend=c("Contra Costa County", "LA County", "Philadelphia County", "Queen's County", "Cook County", "Miami-Dade County", "King County", "Harris County", "Wayne County", "Jefferson County"), col=c("red", "green","orange", "yellow", "purple", "dark green", "brown", "black", "dark red", "blue"), lty=1, cex=0.9)

# Ranked by Temperature
scatter.smooth(HAD$Day,HAD$CasesPerDensity, type="o", col="white",ylim = c(0,6),xlab = "Day", ylab = "Positive Test/Density ", main = "Number of Cases/Density Ranked by Temperature(F)", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$CasesPerDensity~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$CasesPerDensity~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$CasesPerDensity~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$CasesPerDensity~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$CasesPerDensity~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$CasesPerDensity~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$CasesPerDensity~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$CasesPerDensity~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$CasesPerDensity~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)

legend(1,6, legend=c("1.) Miami-Dade", "2.) Harris", "3.) Jefferson", "4.) Los Angeles", "5.) Contra Costa", "6.) Philidelphia", "7.) Queen's", "8.) Cook", "9.) Wayne", "10.) King"), col = c("dark green", "black", "blue", "green", "red", "orange", "yellow", "purple", "dark red", "brown"), lty = 1, cex = 0.9)

# Ranked by Escore
scatter.smooth(HAD$Day,HAD$CasesPerDensity, type="o", col="white",ylim = c(0,6),xlab = "Day", ylab = "Positive Test/Density ", main = "Number of Cases/Density Ranked by Enplanement Score", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$CasesPerDensity~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$CasesPerDensity~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$CasesPerDensity~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$CasesPerDensity~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$CasesPerDensity~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$CasesPerDensity~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$CasesPerDensity~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$CasesPerDensity~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$CasesPerDensity~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)
legend(1, 6, legend=c("1.) Cook", "2.) Los Angeles", "3.) Queen's", "4.) Contra Costa", "5.) King", "6.) Miami-Dade", "7.) Harris", "8.) Wayne", "9.) Philadelphia", "10.) Jefferson"), col=c("purple", "green", "yellow", "red", "brown", "dark green", "black", "dark red", "orange", "blue"), lty=1, cex=0.9)

# Ranked by Mean Distance from an airport
scatter.smooth(HAD$Day,HAD$CasesPerDensity, type="o", col="white",ylim = c(0,6),xlab = "Day", ylab = "Positive Test/Density ", main = "Number of Cases/Density by Mean Dist from Airport", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$CasesPerDensity~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$CasesPerDensity~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$CasesPerDensity~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$CasesPerDensity~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$CasesPerDensity~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$CasesPerDensity~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$CasesPerDensity~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$CasesPerDensity~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$CasesPerDensity~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)
legend(1, 6, legend=c("1.) Miami-Dade", "2.) Los Angeles", "3.) Contra Costa", "4.) Cook", "5.) Harris", "6.) Queen's", "7.) King", "8.) Philadelphia", "9.) Wayne", "10.) Jefferson"), col=c("dark green", "green", "red", "purple", "black", "yellow", "brown", "orange", "dark red", "blue"), lty=1, cex=0.9)

# Ranked by days in quarantine
scatter.smooth(HAD$Day,HAD$CasesPerDensity, type="o", col="white",ylim = c(0,6),xlab = "Day", ylab = "Positive Test/Density ", main = "Number of Cases/Density by Number of Days in Quarantine", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$CasesPerDensity~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$CasesPerDensity~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$CasesPerDensity~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$CasesPerDensity~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$CasesPerDensity~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$CasesPerDensity~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$CasesPerDensity~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$CasesPerDensity~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$CasesPerDensity~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)
legend(1, 6, legend=c("1.) Philadelphia", "2.) Contra Costa", "3.) Los Angeles", "4.) Cook", "5.) Jefferson", "6.) Wayne", "7.) Queen's", "8.) King", "9.) Harris", "10.) Miami-Dade"), col=c("orange", "red", "green", "purple", "blue", "dark red", "yellow", "brown", "black", "dark green"), lty=1, cex=0.9)

# the following would be InfectionsbyDay/Density or slope per square mile
# use this graph to propose further studies for analysis
#   declined after a given amount of time.
#   Explain further analysis of New York and Chicago

par(mfrow = c(2,5))
scatter.smooth(y = JFD$PositiveTestPerDensity, x = JFD$Day, main = "PositiveTestPerDensity/Day JFD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "blue")
scatter.smooth(y = CCD$PositiveTestPerDensity, x = CCD$Day, main = "PositiveTestPerDensity/Day CCD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "red")
scatter.smooth(y = LAD$PositiveTestPerDensity, x = LAD$Day, main = "PositiveTestPerDensity/Day LAD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "green")
scatter.smooth(y = PHD$PositiveTestPerDensity, x = PHD$Day, main = "PositiveTestPerDensity/Day PHD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "orange")
scatter.smooth(y = QND$PositiveTestPerDensity, x = QND$Day, main = "PositiveTestPerDensity/Day QND", ylab = "PositiveTestPerDensity", xlab = "Day", col = "gold")
scatter.smooth(y = CKD$PositiveTestPerDensity, x = CKD$Day, main = "PositiveTestPerDensity/Day CKD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "purple")
scatter.smooth(y = MDD$PositiveTestPerDensity, x = MDD$Day, main = "PositiveTestPerDensity/Day MDD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "dark green")
scatter.smooth(y = KGD$PositiveTestPerDensity, x = KGD$Day, main = "PositiveTestPerDensity/Day KGD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "brown")
scatter.smooth(y = HAD$PositiveTestPerDensity, x = HAD$Day, main = "PositiveTestPerDensity/Day HAD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "black")
scatter.smooth(y = WAD$PositiveTestPerDensity, x = WAD$Day, main = "PositiveTestPerDensity/Day WAD", ylab = "PositiveTestPerDensity", xlab = "Day", col = "dark red")

# final Proposition graph
# use this graph to propose further studies for analysis
# compare and mark each counties applied quarantine and observe if the infection rates
#   declined after a given amount of time.
par(mfrow = c(1,1))
scatter.smooth(HAD$Day,HAD$PositiveTestPerDensity, type="o", col="white",ylim = c(0,0.35),xlab = "Day", ylab = "Rate", main = "Day-by-Day Rate of Increase/Density", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(CCD$PositiveTestPerDensity~CCD$Day)
lines(predict(lo), col="red", lwd=2)
lo <- loess(LAD$PositiveTestPerDensity~LAD$Day)
lines(predict(lo), col="green", lwd=2)
lo <- loess(PHD$PositiveTestPerDensity~PHD$Day)
lines(predict(lo), col="orange", lwd=2)
lo <- loess(QND$PositiveTestPerDensity~QND$Day)
lines(predict(lo), col="yellow", lwd=2)
lo <- loess(CKD$PositiveTestPerDensity~CKD$Day)
lines(predict(lo), col="purple", lwd=2)
lo <- loess(MDD$PositiveTestPerDensity~MDD$Day)
lines(predict(lo), col="dark green", lwd=2)
lo <- loess(KGD$PositiveTestPerDensity~KGD$Day)
lines(predict(lo), col="brown", lwd=2)
lo <- loess(JFD$PositiveTestPerDensity~JFD$Day)
lines(predict(lo), col="blue", lwd=2)
lo <- loess(WAD$PositiveTestPerDensity~WAD$Day)
lines(predict(lo), col="dark red", lwd=2)
legend(0, 0.35, legend=c("Contra Costa County", "LA County", "Philadelphia County", "Queen's County", "Cook County", "Miami-Dade County", "King County", "Harris County", "Wayne County", "Jefferson County"), col=c("red", "green","orange", "yellow", "purple", "dark green", "brown", "black", "dark red", "blue"), lty=1, cex=0.75)

#*****

```

# Factors that Affect the graphs above
# Testing and time of documentation of cases may have affected the graphs above

```{r Chicago and NY expanded}
#5# Queens County starts on March 16th the length will be adjusted for to match Chicago #######################################################################
#5# Queens County starts on March 16th the length will be adjusted for to match Chicago #######################################################################
ExQND <- subset(zdata, zdata$State == "NY" & zdata$County.Name == "Queens County")
ExQND <- ExQND[5:length(ExQND)]
ExQND <- t(ExQND)
colnames(ExQND) <- "Cases"
ExQND <- as.data.frame(ExQND)
ExQND <- subset(ExQND, ExQND$Cases > 100 & ExQND$Cases < 53100)

ExQND$Day <- 0:47
ExQND[,c("Day","Cases")] -> ExQND
ExQND$Escore <- rep(29.5,48)
ExQND$MeanDistance<-rep(16.30,48)
ExQND$Area<-rep(109,48)
ExQND$Population <- rep(2.273,48)
ExQND$Population/ExQND$Area -> ExQND$Density
ExQND$DaysClosed <- rep(42,48)

tempv <- sequence(48)
x <- sequence(48)
for(i in x){
  tempv[i] <- (ExQND$`Cases`[i+1] - ExQND$`Cases`[i])}

ExQND$InfectionsByDay <- tempv
ExQND$InfectionsByDay / ExQND$Population -> ExQND$PositiveTestPerPop
rep(mean(ExQND$PositiveTestPerPop[1:47]),48) -> ExQND$AverageInfPerDay
ExQND$AverageInfPerDay/ExQND$Population -> ExQND$AvInfPerPop
ExQND$Cases / ExQND$Area -> ExQND$CasesPerArea
ExQND$Cases / (ExQND$Density*1000000) -> ExQND$CasesPerDensity
ExQND$InfectionsByDay / ExQND$Area -> ExQND$PositiveTestPerArea
ExQND$InfectionsByDay / (ExQND$Density*1000000) -> ExQND$PositiveTestPerDensity

#6# Cook County starts on March 17th  #########################################################################

ExCKD <- subset(zdata, zdata$State == "IL" & zdata$County.Name == "Cook County")
ExCKD <- ExCKD[5:length(ExCKD)]
ExCKD <- t(ExCKD)
colnames(ExCKD) <- "Cases"
ExCKD <- as.data.frame(ExCKD)
ExCKD <- subset(ExCKD, ExCKD$Cases > 100)

ExCKD$Day <- 0:47
ExCKD[,c("Day","Cases")] -> ExCKD
ExCKD$Escore <- rep(76.8,48)
ExCKD$MeanDistance<-rep(15.87,48)
ExCKD$Area<-rep(945,48)
ExCKD$Population <- rep(5.15,48)
ExCKD$Population/ExCKD$Area -> ExCKD$Density
ExCKD$DaysClosed <- rep(44,48)

tempv <- sequence(48)
x <- sequence(48)
for(i in x){
  tempv[i] <- (ExCKD$`Cases`[i+1] - ExCKD$`Cases`[i])}

ExCKD$InfectionsByDay <- tempv
ExCKD$InfectionsByDay / ExCKD$Population -> ExCKD$PositiveTestPerPop
rep(mean(ExCKD$PositiveTestPerPop[1:47]),48) -> ExCKD$AverageInfPerDay
ExCKD$AverageInfPerDay/ExCKD$Population -> ExCKD$AvInfPerPop
ExCKD$Cases / ExCKD$Area -> ExCKD$CasesPerArea
ExCKD$Cases / (ExCKD$Density*1000000) -> ExCKD$CasesPerDensity
ExCKD$InfectionsByDay / ExCKD$Area -> ExCKD$PositiveTestPerArea
ExCKD$InfectionsByDay / (ExCKD$Density*1000000) -> ExCKD$PositiveTestPerDensity

scatter.smooth(ExQND$Day,ExQND$Cases, type="o", col="white",ylim = c(0,55000),xlab = "Day", ylab = "Confirmed Cases", main = "Covid-19 Cases", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(ExCKD$Cases~ExCKD$Day)
lines(predict(lo), col="green", lwd=2)
legend(0, 50000, legend=c("Queen's County", "Cook County"), col=c("black", "green"), lty=1, cex=0.85)

scatter.smooth(ExQND$Day,ExQND$CasesPerDensity, type="o", col="white",ylim = c(0,8),xlab = "Day", ylab = "Positive Test/Density ", main = "Number of Cases/Density", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(ExCKD$CasesPerDensity~ExCKD$Day)
lines(predict(lo), col="green", lwd=2)
legend(0, 7, legend=c("Queen's County", "Cook County"), col=c("black", "green"), lty=1, cex=0.85)

scatter.smooth(ExQND$Day,ExQND$PositiveTestPerDensity, type="o", col="white",ylim = c(0,0.4),xlab = "Day", ylab = "Rate", main = "Day-by-Day Rate of Increase/Density", lwd = 2)
grid(nx = NULL, ny = NULL, col = "darkgray", lty = "dotted")
lo <- loess(ExCKD$PositiveTestPerDensity~ExCKD$Day)
lines(predict(lo), col="green", lwd=2)
legend(0, 0.35, legend=c("Queen's County", "Cook County"), col=c("black", "green"), lty=1, cex=0.85)

```

Summary


Results & Discussion: 

Was the hypothesis proven to be true or void?
Talk of ten counites and how they are related or how they were used for this particular study.

Discuss Graphs, 
  Pairs shows correlations
  Linear regression shows further correlation to density
  ...
  
  Explain that the other possible correlations are not necessarily clear since there are not enough data points
  
  
  









